Biotic invasions fuck with the manageability of pollination networks

### 2017-01-17 paper/draft_2.Rmd
Minor changes to the methods

Finding the maximum matchings can be an expensive operation especially in large, directed, and highly connected networks.
Although less computationally expensive heuristics to characterise the control profile of complex networks do exist [@Ruths2014], we found their use to be extremely sensitive to assumptions regarding the direction of control (Supplementary Materials Section 2).
Consequently, we have adopted a strategy based on an alternative bipartite representation of the directed network in which the two levels indicate the outgoing and incoming links to each node (Supplementary Section XXX). 
Once we had this alternative representation, then used the maximum bipartite matching algorithm implemented in `igraph` on each empirica [@Csardi2006a].

@@

We next explored whether real networks differ in their architecture from random ones in a concerted way that affects manageability. 
Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship have not been tested for in weighted ecological networks. 
We therefore compared the driver node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary. 
Randomisations were generated using vegan 2.3-3 [@Oksanen2016]. 
After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~*  using our maximum matching framework.
Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding one of each set of 999 randomisations.

>>>>

Finding the maximum matchings can be an expensive operation especially in large, directed, and highly connected networks.
Although less computationally expensive heuristics to approximate the control profile of complex networks do exist [@Ruths2014], we found their use to be extremely sensitive to assumptions regarding the direction of control (Supplementary Materials Section 2).
Consequently, we have adopted a strategy based on an alternative bipartite representation of the directed network in which the two levels indicate the outgoing and incoming links to each node (Supplementary Section XXX). 
Once we had this alternative representation, then, on each network, we used the maximum bipartite matching algorithm implemented in the `max_bipartite_match` function of igraph 1.0.1 [@Csardi2006a].

@@

We next explored whether real networks differ in their architecture from random ones in a concerted way that affects manageability. 
Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship have not been tested for in weighted ecological networks. 
We therefore compared the driver node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary. 
Randomisations were generated using the function `commsim` in vegan 2.3-3 [@Oksanen2016]. 
After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~*  using our maximum matching framework.
Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding one of each set of 999 randomisations.
